### 2020-07-16 paper.tex
Rewrite abstract

\begin{abstract}
Involutive MCMC is a unifying framework for MCMC that encompasses many standard
and recent MCMC algorithms from the literature, from reversible jump MCMC to
Hamiltonian Monte Carlo to kernels based on deep neural networks. The key idea
in involutive MCMC is that a combination of (i) an auxiliary probability
distribution and (ii) an involution on the extended state space that includes
the model latent variables and the auxiliary variables results in MCMC kernels
that satisfy detailed balance with respect to the target distribution. The
involutive MCMC framework is appealing for its simplicity and generality, and
promises to be a useful conceptual and mathematical tool for exploring the
design space of MCMC kernels. However, like other Monte Carlo samplers,
implementing involutive samplers is time consuming and error prone. This paper
describes a technique for automatically generating the implementation of
involutive MCMC samplers from two probabilistic programs that define the target
distribution and the auxiliary probability distribution respectively, and a
differentiable program that defines the involution. The technique also detects
common conceptual and programming errors that arise when designing and
specifying involutive MCMC algorithms. This paper describes the support for
involutive MCMC in the Gen probabilistic system that uses this technique, and
shows involutive samplers specified using Gen's high-level probabilistic and
differentiable programming languages.
\end{abstract}

>>>>

\begin{abstract}
Involutive MCMC is a unifying mathematical construction for MCMC kernels that generalizes many classic and state-of-the-art MCMC algorithms, from reversible jump MCMC to kernels based on deep neural networks.
But like MCMC samplers more generally, implementing involutive MCMC kernels is often tedious and error-prone, especially when sampling on complex state spaces.
This paper describes a technique for automating the implementation of involutive MCMC kernels given (i) a pair of probabilistic programs defining the target distribution and an auxiliary distribution respectively and (ii) a differentiable program that transforms the execution traces of these probabilistic programs.
The technique, which is implemented as part of the Gen probabilistic programming system, also automatically detects user errors in the specification of involutive MCMC kernels and exploits sparsity in the kernels for improved efficiency.
The paper shows example Gen code for a split-merge reversible jump move in an infinite Gaussian mixture model and a state-dependent mixture of proposals on a combinatorial space of covariance functions for a Gaussian process.
\end{abstract}
